Language-Based Security for Low-Level MPC

### 2024-05-17 ppdp24/main.tex
tiny tweaks and a note
checkpoint

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}
\usepackage{thmtools,thm-restate}
\usepackage{comment}
\usepackage{booktabs,array}
\usepackage{rotating}

@@

\author{Joseph Near}
\affiliation{
  \institution{University of Vermont}
  \city{}
  \country{}
%  \city{Burlington}
%  \country{USA}
}
\email{jnear@uvm.edu}

\begin{abstract}
  Secure Multi-Party Computation (MPC) protocols is an important
  enabling technology for data privacy in modern distributed
  applications. Currently, proof methods for low-level MPC protocols
  are primarily manual and thus tedious and error-prone, and are also
  non-standardized and unfamiliar to most PL theorists. As a step
  towards better language support and language-based enforcement, we
  develop a new staged PL for defining a variety of low-level
  probabilistic MPC protocols. We also formulate a collection of
  confidentiality and integrity hyperproperties for our language model
  that are familiar from information flow, including conditional
  noninterference, delimited release, and robust declassification. We
  demonstrate their relation to standard MPC threat models of passive
  and malicious security, and how they can be leveraged in security
  verification of protocols. To prove these properties we develop
  automated tactics in $\mathbb{F}_2$ that can be integrated with
  separation-logic style reasoning.
\end{abstract}

>>>>

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}
\usepackage{thmtools,thm-restate}
\usepackage{comment}
\usepackage{booktabs,array}
\usepackage{rotating}
\usepackage{xcolor}

@@

\author{Joseph P. Near}
\affiliation{
  \institution{University of Vermont}
  \city{}
  \country{}
%  \city{Burlington}
%  \country{USA}
}
\email{jnear@uvm.edu}

\begin{abstract}
  Secure Multi-Party Computation (MPC) is an important
  enabling technology for data privacy in modern distributed
  applications. Currently, proof methods for low-level MPC protocols
  are primarily manual and thus tedious and error-prone, and are also
  non-standardized and unfamiliar to most PL theorists. As a step
  towards better language support and language-based enforcement, we
  develop a new staged PL for defining a variety of low-level
  probabilistic MPC protocols. We also formulate a collection of
  confidentiality and integrity hyperproperties for our language model
  that are familiar from information flow, including conditional
  noninterference, delimited release, and robust declassification. We
  demonstrate their relation to standard MPC threat models of passive
  and malicious security, and how they can be leveraged in security
  verification of protocols. To prove these properties we develop
  automated tactics in $\mathbb{F}_2$ that can be integrated with
  separation logic-style reasoning.
\end{abstract}
